Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-09 paper/main.tex
Updates
udpates

@@

Points:
\begin{itemize}
	\item As researchers prefer to anyways build models by hand, this is like a companion tool to help them in deciding the method.
	\item Solves all the $ 3 $ issues outlined in the introduction.
	\item Compared to other expert knowledge specification methods, users don't need to guess what information then need to provide as exact questions are asked. Also enables us to ask an LLM for it.
\end{itemize}

>>>>

As at any iteration, multiple changes to the DAG are possible. We also give a
way to rank potential new edges additions to the DAG using effect size measures
for CI tests.

@@

Points:
\begin{itemize}
	\item As researchers prefer to build models by hand, we present a tool
		to assist them in construction using CI testing.
	\item In practice as many edges are possible for any given DAG, we provide
		a ranking method to find the best edge addition.
	\item Compared to other expert knowledge specification methods, users
		don't need to guess what information then need to provide as
		exact questions are asked. Also enables us to ask an LLM for
		it.
\end{itemize}
